Supplementary Document 2

### 2018-05-16 inst/supp_doc2/supp_doc2.Rmd
updating all paths to figure numbers
adding rmd for supp doc 2

---
title: "Primers"
author: "Jason T. Serviss"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    code_folding: hide
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}

library(printr)
library(tibble)

```

## Figure 1b

```{r}

tibble(
    name=c(
        "miR34a asRNA F1",
        "miR34a asRNA R1",
        "miR34a HG F",
        "miR34a HG R",
        "ß-actin Fwd",
        "ß-actin Rev"
    ),
    sequence=c(
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)

```

@@

```{r}

tibble(
  name = c(
    "miR34a asRNA F10",
    "polyT T7 FAM",
    "miR34a asRNA F1",
    "FAM primer"),
  sequence = c(
    "ACG CGT CTC TCC AGC CCG GGA T",
    "CAG TGA ATT GTA ATA CGA CTC ACT ATA GGG ACA TCC GTA GCT CGT CCA GGA CCC TTT TTT TTT TTT TTT TTT VN",
    "AGC GGC ATC TCC TCC ACC TGA AA",
    "CCG TAG CTC GTC CAG GAC CC"
  )
)

```

@@

```{r}

tibble(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a HG F",
        "miR34a HG R",
        "miR34a AS F1",
        "miR34a AS R1"

    ),
    sequence=c(
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TCG GGA TGT CCA CGT CA",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT"

    )
)

```

@@

```{r}

tibble(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a HG F",
        "miR34a HG R",
        "miR34a as F1",
        "miR34a as R1"

    ),
    sequence=c(
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TCG GGA TGT CCA CGT CA",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT"

    )
)

```

@@

```{r}

tibble(
    name=c(
        "Luc setII F",
        "Luc setII R",
        "Renilla pBiDir F1",
        "Renilla pBiDir R1",
        "ß-actin Fwd",
        "ß-actin Rev"
    ),
    sequence=c(
        "AAG ATT CAA AGT GCG CTG CTG",
        "TTG CCT GAT ACC TGG CAG ATG",
        "TAA CGC GGC CTC TTC TTA TTT",
        "GAT TTG CCT GAT TTG CCC ATA",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)

```

@@

```{r}

tibble(
    name=c(
        "Luc set II F",
        "Luc set II R",
        "Renilla pBiDir F1",
        "Renilla pBiDir R1",
        "ß-actin Fwd",
        "ß-actin Rev"
    ),
    sequence=c(
        "AAG ATT CAA AGT GCG CTG CTG",
        "TTG CCT GAT ACC TGG CAG ATG",
        "TAA CGC GGC CTC TTC TTA TTT",
        "GAT TTG CCT GAT TTG CCC ATA",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)

```

@@

Cloning primers

```{r}

tibble(
    name=c(
        "miR34aAS cloning F4",
        "miR34aAS cloning Ex3_1"
    ),
    sequence=c(
        "ACG CGT CTC TCC AGC CCG GGA T",
        "AAT GAT GGC CGC AAC TAA TGA CGG"
    )
)

```

QPCR primers

```{r}

tibble(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a AS F1",
        "miR34a AS R1"

    ),
    sequence=c(
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TCG GGA TGT CCA CGT CA",
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT"

    )
)

```

@@

```{r}

tibble(
    name=c(
        "miR34a ChIP F1",
        "miR34a ChIP R1"
    ),
    sequence=c(
       "AAA GTT TGC AAA GAA GGA GGC GGG",
       "AGG GAA GAA AGA ACT AGC CGA GCA"
    )
)

```

## Figure 1 Supplement 2a

```{r}

tibble(
    name=c(
        "miR34a AS F10",
        "miR34a AS F11",
        "miR34a AS F12",
        "miR34a AS F13",
        "miR34a AS F14",
        "miR34a AS F15",
        "miR34a AS R1"
    ),
    sequence=c(
        "ACG CGT CTC TCC AGC CCG GGA T",
        "ATC TGC GTG GTC ACC GAG AAG CA",
        "CGC ACG GAC TGA GAA ACA CAA G",
        "ACG GAG GCT ACA CAA TTG AAC AGG",
        "AGG GAA GAA AGA ACT AGC CGA GCA",
        "CAT TTG CTG CAA TAT CAC CGT GGC",
        "TTG CCT CGT GAG TCC AAG GAG AAT"
    )
)

```

## Figure 1 Supplement 2b

```{r}

tibble(
    name=c(
        "miR34a AS F1",
        "miR34a AS R1",
        "miR34a AS int1 R1",
        "miR34a HG F",
        "miR34a HG R",
        "ß-actin Fwd",
        "ß-actin Rev",
        "U48 F",
        "U48 R"
    ),
    sequence=c(
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT",
        "TGC GCA AAC TAC GCG CTC T",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA",
        "AGT GAT GAT GAC CCC AGG TA",
        "GGT CAG AGC GCT GCG GTG AT"
    )
)

```

## Figure 1 Supplement 2c

```{r}

tibble(
    name=c(
        "miR34a AS F12",
        "miR34a AS R1",
        "miR34a AS R2",
        "miR34a AS R3",
        "miR34a AS Ex3 R1"
    ),
    sequence=c(
        "AAA CAC AAG CGT TTA CCT GGG TGC",
        "TTG CCT CGT GAG TCC AAG GAG AAT",
        "ATA GGT TCA TTT GCC CGA TGT GCC",
        "CCA CAG CTG TTG CTT CTG AAT GCT",
        "TGA TGG CCG CAA CTA ATG ACG GAT"
    )
)

```

## Figure 2 Supplement 2a

```{r}

 tibble(
    name=c(
        "Luc setII F",
        "Luc setII R",
        "Renilla pBiDir F1",
        "Renilla pBiDir R1",
        "ß-actin Fwd",
        "ß-actin Rev"
    ),
    sequence=c(
        "AAG ATT CAA AGT GCG CTG CTG",
        "TTG CCT GAT ACC TGG CAG ATG",
        "TAA CGC GGC CTC TTC TTA TTT",
        "GAT TTG CCT GAT TTG CCC ATA",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)

```

## Figure 3 Supplement 1a

Cloning primers

```{r}

tibble(
    name=c(
        "miR34aAS cloning F4",
        "miR34aAS cloning Ex3_1"
    ),
    sequence=c(
        "ACG CGT CTC TCC AGC CCG GGA T",
        "AAT GAT GGC CGC AAC TAA TGA CGG"
    )
)

```

QPCR primers

```{r}

tibble(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a AS F1",
        "miR34a AS R1"

    ),
    sequence=c(
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TCG GGA TGT CCA CGT CA",
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT"

    )
)
```

## Figure 3 Supplement 2a

```{r}

tibble(
    name=c(
        "CCND1 Fwd",	
        "CCND1 Rev",
        "ß-actin Fwd",
        "ß-actin Rev"
    ),
    sequence=c(
        "CGT GGC CTC TAA GAT GAA GG",
        "CTG GCA TTT TGG AGA GGA AG",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)

```

>>>>

---
title: "Supplementary Document 2"
output: html_document
---

## Figure 1b
###

| name             | sequence                         |
| ---------------- |:--------------------------------:|
| miR34a asRNA F1  | AGC GGC ATC TCC TCC ACC TGA AA   |
| miR34a asRNA R1  | TTG CCT CGT GAG TCC AAG GAG AAT  |
| miR34a HG F      | TCT GCT CCA GTG GCT GAT GAG AAA  |
| miR34a HG R      | GTT CAC TGG CCT CAA AGT TGG CAT  |
| ß-actin Fwd      | AGG TCA TCA CCA TTG GCA ATG AG   |
| ß-actin Rev      | CTT TGC GGA TGT CCA CGT CA       |

@@

| name              | sequence                                                                                            |
| ----------------- |:---------------------------------------------------------------------------------------------------:|
| miR34a asRNA F10  | ACG CGT CTC TCC AGC CCG GGA T                                                                       |
| polyT T7 FAM      | CAG TGA ATT GTA ATA CGA CTC ACT ATA GGG ACA TCC GTA GCT CGT CCA GGA CCC TTT TTT TTT TTT TTT TTT VN  |
| miR34a asRNA F1   | AGC GGC ATC TCC TCC ACC TGA AA                                                                      |
| FAM primer        | CCG TAG CTC GTC CAG GAC CC                                                                          |

@@

| name          | sequence                         |
| ------------- |:--------------------------------:|
| ß-actin Fwd   | AGG TCA TCA CCA TTG GCA ATG AG   |
| ß-actin Rev   | CTT TCG GGA TGT CCA CGT CA       |
| miR34a HG F   | TCT GCT CCA GTG GCT GAT GAG AAA  |
| miR34a HG R   | GTT CAC TGG CCT CAA AGT TGG CAT  |
| miR34a AS F1  | AGC GGC ATC TCC TCC ACC TGA AA   |
| miR34a AS R1  | TTG CCT CGT GAG TCC AAG GAG AAT  |

@@

| name          | sequence                         |
| ------------- |:--------------------------------:|
| ß-actin Fwd   | AGG TCA TCA CCA TTG GCA ATG AG   |
| ß-actin Rev   | CTT TCG GGA TGT CCA CGT CA       |
| miR34a HG F   | TCT GCT CCA GTG GCT GAT GAG AAA  |
| miR34a HG R   | GTT CAC TGG CCT CAA AGT TGG CAT  |
| miR34a AS F1  | AGC GGC ATC TCC TCC ACC TGA AA   |
| miR34a AS R1  | TTG CCT CGT GAG TCC AAG GAG AAT  |

@@

**QPCR primers**

| name          | sequence                         |
| ------------- |:--------------------------------:|
| ß-actin Fwd   | AGG TCA TCA CCA TTG GCA ATG AG   |
| ß-actin Rev   | CTT TCG GGA TGT CCA CGT CA       |
| miR34a HG F   | TCT GCT CCA GTG GCT GAT GAG AAA  |
| miR34a HG R   | GTT CAC TGG CCT CAA AGT TGG CAT  |
| miR34a AS F1  | AGC GGC ATC TCC TCC ACC TGA AA   |
| miR34a AS R1  | TTG CCT CGT GAG TCC AAG GAG AAT  |

@@

| name               | sequence                        |
| ------------------ |:-------------------------------:|
| Luc setII F        | AAG ATT CAA AGT GCG CTG CTG     |
| Luc setII R        | TTG CCT GAT ACC TGG CAG ATG     |
| Renilla pBiDir F1  | TAA CGC GGC CTC TTC TTA TTT     |
| Renilla pBiDir R1  | GAT TTG CCT GAT TTG CCC ATA     |
| ß-actin Fwd        | AGG TCA TCA CCA TTG GCA ATG AG  |
| ß-actin Rev        | CTT TGC GGA TGT CCA CGT CA      |

## Figure 2e

| name               | sequence                        |
| ------------------ |:-------------------------------:|
| Luc setII F        | AAG ATT CAA AGT GCG CTG CTG     |
| Luc setII R        | TTG CCT GAT ACC TGG CAG ATG     |
| Renilla pBiDir F1  | TAA CGC GGC CTC TTC TTA TTT     |
| Renilla pBiDir R1  | GAT TTG CCT GAT TTG CCC ATA     |
| ß-actin Fwd        | AGG TCA TCA CCA TTG GCA ATG AG  |
| ß-actin Rev        | CTT TGC GGA TGT CCA CGT CA      |

@@

**Cloning primers**

| name                    | sequence                         |
| ----------------------- |:--------------------------------:|
| miR34aAS cloning F4     | ACG CGT CTC TCC AGC CCG GGA T    |
| miR34aAS cloning Ex3_1  | AAT GAT GGC CGC AAC TAA TGA CGG  |

**QPCR primers**

| name         | sequence                         |
| ------------ |:--------------------------------:|
| ß-actin Fwd  | AGG TCA TCA CCA TTG GCA ATG AG   |
| ß-actin Rev  | CTT TCG GGA TGT CCA CGT CA       |
| miR34a AS F1 |  AGC GGC ATC TCC TCC ACC TGA AA  |
| miR34a AS R1 |  TTG CCT CGT GAG TCC AAG GAG AAT |

@@

| name            | sequence                         |
| --------------- |:--------------------------------:|
| miR34a ChIP F1  | AAA GTT TGC AAA GAA GGA GGC GGG  |
| miR34a ChIP R1  | AGG GAA GAA AGA ACT AGC CGA GCA  |

## Supplementary Figure 2a

| name           | sequence                         |
| -------------- |:--------------------------------:|
| miR34a AS F10  | ACG CGT CTC TCC AGC CCG GGA T    |
| miR34a AS F11  | ATC TGC GTG GTC ACC GAG AAG CA   |
| miR34a AS F12  | CGC ACG GAC TGA GAA ACA CAA G    |
| miR34a AS F13  | ACG GAG GCT ACA CAA TTG AAC AGG  |
| miR34a AS F14  | AGG GAA GAA AGA ACT AGC CGA GCA  |
| miR34a AS F15  | CAT TTG CTG CAA TAT CAC CGT GGC  |
| miR34a AS R1   | TTG CCT CGT GAG TCC AAG GAG AAT  |

## Supplementary Figure 2b

| name               | sequence                         |
| ------------------ |:--------------------------------:|
| miR34a AS F1       | AGC GGC ATC TCC TCC ACC TGA AA   |
| miR34a AS R1       | TTG CCT CGT GAG TCC AAG GAG AAT  |
| miR34a AS int1 R1  | TGC GCA AAC TAC GCG CTC T        |
| miR34a HG F        | TCT GCT CCA GTG GCT GAT GAG AAA  |
| miR34a HG R        | GTT CAC TGG CCT CAA AGT TGG CAT  |
| ß-actin Fwd        | AGG TCA TCA CCA TTG GCA ATG AG   |
| ß-actin Rev        | CTT TGC GGA TGT CCA CGT CA       |
| U48 F              | AGT GAT GAT GAC CCC AGG TA       |
| U48 R              | GGT CAG AGC GCT GCG GTG AT       |

## Supplementary Figure 2c

| name              | sequence                         |
| ----------------- |:--------------------------------:|
| miR34a AS F12     | AAA CAC AAG CGT TTA CCT GGG TGC  |
| miR34a AS R1      | TTG CCT CGT GAG TCC AAG GAG AAT  |
| miR34a AS R2      | ATA GGT TCA TTT GCC CGA TGT GCC  |
| miR34a AS R3      | CCA CAG CTG TTG CTT CTG AAT GCT  |
| miR34a AS Ex3 R1  | TGA TGG CCG CAA CTA ATG ACG GAT  |

## Supplementary Figure 3c

| name               | sequence                        |
| ------------------ |:-------------------------------:|
| Luc setII F        | AAG ATT CAA AGT GCG CTG CTG     |
| Luc setII R        | TTG CCT GAT ACC TGG CAG ATG     |
| Renilla pBiDir F1  | TAA CGC GGC CTC TTC TTA TTT     |
| Renilla pBiDir R1  | GAT TTG CCT GAT TTG CCC ATA     |
| ß-actin Fwd        | AGG TCA TCA CCA TTG GCA ATG AG  |
| ß-actin Rev        | CTT TGC GGA TGT CCA CGT CA      |

## Supplementary Figure 4a

**Cloning primers**

| name                    | sequence                         |
| ----------------------- |:--------------------------------:|
| miR34aAS cloning F4     | ACG CGT CTC TCC AGC CCG GGA T    |
| miR34aAS cloning Ex3_1  | AAT GAT GGC CGC AAC TAA TGA CGG  |

**QPCR primers**

| name          | sequence                         |
| ------------- |:--------------------------------:|
| ß-actin Fwd   | AGG TCA TCA CCA TTG GCA ATG AG   |
| ß-actin Rev   | CTT TCG GGA TGT CCA CGT CA       |
| miR34a AS F1  | AGC GGC ATC TCC TCC ACC TGA AA   |
| miR34a AS R1  | TTG CCT CGT GAG TCC AAG GAG AAT  |

## Supplementary Figure 4c

| name         | sequence                        |
| ------------ |:-------------------------------:|
| CCND1 Fwd    | CGT GGC CTC TAA GAT GAA GG      |
| CCND1 Rev    | CTG GCA TTT TGG AGA GGA AG      |
| ß-actin Fwd  | AGG TCA TCA CCA TTG GCA ATG AG  |
| ß-actin Rev  | CTT TGC GGA TGT CCA CGT CA      |
